---
title: "Report Calm Study"
format: docx
editor: visual
---

## Data

There are 4 different conditions of interest and one placebo group. Each group contains 20 subjects for a total of 100 subjects.

We consider a total of 29 different endpoints. 18 endpoints related to MOOD (10 component scores and 8 aggregate scores), 2 endpoints of NASA-TLX aggregate scores (raw and weighted), 1 endpoint measuring cortisol levels in saliva, 7 endpoints of the STAI short form (6 component scores and 1 aggregate score) and finally 1 endpoint concerning stress VAS.

For each subject, each endpoint is measured 4 times: baseline pre stressor event, baseline post stressor event, treatment pre stressor event and treatment post stressor event. For each measurement the difference $\Delta = x_{post} - x_{pre}$ is calculated for both the baseline and treatment measurements.

### Missing Data

Missing data is minimal. Treatment data of subject 108/N-Z (treatment: P) is not available. In addition, for subjects 001/M-B (treatment: S) and 025/M-E (Treatment: P) Baseline saliva cortisol levels are not available and for subjects 030/S-H (Treatment: T) and 085/I-J (Treatment: P) both baseline and treatment cortisol levels are not available.

We will consider missing data as missing completely at random.

## Methods

All measurements are treated as continuous, except for the STAI component variables. Since these outcome variables are integers with a narrow range, we opt to treat them as an ordinal variable. The overall STAI score is considered continuous.

If necessary, other integer outcome variables can be treated as ordinal variables if the range of outcomes is small.

For the continuous outcome variables, a linear model (lm) is fitted which quantifies the effect of the SPID, while controlling for baseline difference, sex and age. Model assumptions are assesed visually with plots.

For the ordinal outcome variables a cumulative link model (clm) is fitted which quantifies the effect of the SPID, while controlling for baseline difference, sex and age. The proportional odds assumption are assesed with nominal_test(). Homoscedacity is assessed with the scale_test().

We will report the effect size estimate and p-value of each treatment on each outcome. For estimates of clm's we will also report exponentiated coefficients. We will provide both uncorrected p-values as well as a Benjamini-Hochberg corrected p-values.

## Results

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)
```

```{r libraries}
suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(here)
  library(ordinal)
  library(sure)
})
```

```{r load_helpers}
source(here("scripts", "helpers.R"))
```

```{r load_data}
data_path <- here("data", "test")
data_files <- list.files(data_path, pattern = "\\.rds$", full.names = TRUE)

if (length(data_files) == 0) {
  stop("No .rds datasets found in data/test.")
}

data_list <- lapply(data_files, readRDS)
names(data_list) <- tools::file_path_sans_ext(basename(data_files))

tibble::tibble(
  n_datasets = length(data_list),
  first_dataset = names(data_list)[1]
)
```

```{r run_models}
# Integer outcomes with <= 6 unique values are modeled as ordinal outcomes.
narrow_range_unique_value_cutoff <- 6

results <- lapply(names(data_list), function(dataset_name) {
  analyze_dataset(
    data_list[[dataset_name]],
    dataset_name,
    cutoff = narrow_range_unique_value_cutoff
  )
})
names(results) <- names(data_list)
```

```{r spid_summary}
missing_spid_coef <- names(results)[!vapply(results, function(x) "spid_coef" %in% names(x), logical(1))]
if (length(missing_spid_coef) > 0) {
  stop(
    sprintf(
      paste(
        "Missing spid_coef in results for: %s.",
        "This typically indicates a failed model fit or incomplete output from analyze_dataset().",
        "Review model diagnostics for the listed datasets and rerun the analysis.",
        sep = "\n"
      ),
      paste(missing_spid_coef, collapse = ", ")
    )
  )
}

spid_summary <- bind_rows(lapply(results, function(x) x$spid_coef)) |>
  mutate(adjusted_p_value = p.adjust(p_value, method = "BH")) |>
  arrange(adjusted_p_value)

spid_summary |>
  select(dataset, model_type, term, estimate, std_error, statistic, p_value, adjusted_p_value)
```
